\documentclass{cv}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[left=1.0in,top = 1.0in,right=1.0in,bottom=1.0in]{geometry} % Document margins

\usepackage{fancyhdr,tabularx}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{14pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{hyperref}
\name{Isaac Malsky}
\phone{\href{github.com/imalsky}{github.com/imalsky}}
\email{isaacmalsky@gmail.com}
\renewcommand{\familydefault}{\sfdefault} %edit this for fonts


\begin{document}
\vspace{-0.1cm}
\begin{cSection}{Education}
\begin{cSubsection}{\vspace{1.6em} Ph.D., Astronomy and Astrophysics} {The University of Michigan\hspace{-0.5em}} {\normalfont{Advisor: Prof. Emily Rauscher}} {2019-2024}
\item Dissertation: ``Modeling the 3D Atmospheric Structure of Hot Gaseous Planets''
\end{cSubsection}
\vspace{-0.1cm}
\begin{cSubsection}{B.A., Physics, with honors} {The University of Chicago\hspace{-0.5em}}
{\normalfont{ Thesis: ``The Coupled Thermal and Compositional Evolution of Planet Envelopes''}}{2014--2018  }
\item
\vspace{-0.8cm}
\end{cSubsection}
\end{cSection}


\vspace{-0.1cm}
\begin{cSection}{Appointments}

\begin{cSubsection}{\vspace{1.6em}NASA Jet Propulsion Laboratory}{Pasadena, California\hspace{-0.5em}}{Postdoctoral Researcher}{2024 - present}\item \emph{NASA Postdoctoral Program Fellow, Science Division}
\end{cSubsection}

\vspace{-0.1cm}
\begin{cSubsection}{The University of Michigan}{Ann Arbor, Michigan\hspace{-0.5em}}{Graduate Researcher}{2019 - 2024}\item \emph{Rauscher Lab}
\end{cSubsection}

\vspace{-0.1cm}
\begin{cSubsection}{The University of Chicago}{Chicago, Illinois\hspace{-0.5em}}{Research Assistant}{November 2015 - June 2019}\item \emph{Rogers Lab}
\end{cSubsection}

\vspace{-0.1cm}
\begin{cSubsection}{Argonne National Lab}{Lemont, IL\hspace{-0.5em}}
{Post-bac Researcher}{June 2018 - January 2019} \item \emph{Chan Lab, Center for Nanoscale Materials}
\end{cSubsection}

%\vspace{-0.1cm}
%\begin{cSubsection}{NASA Goddard}{Greenbelt, Maryland}
%{Undergraduate Researcher}{June 2016 - August 2016}
%\item Created a CAD model of a flight dewar and analyzed the performance of sensor equipment when cooled with liquid helium.
%\end{cSubsection}

\end{cSection}
\vspace{-0.2cm}

%\begin{cSection}{Skills}
%\item \textit{Languages}: Python, FORTRAN, Bash, Git, C/C++ (OpenMP), MATLAB
%\vspace{-0.2cm}
%\item \textit{Libraries}{: pandas, NumPy, Matplotlib, SciPy}
%\end{cSection}




\begin{cSection}{Publications}
\InputIfFileExists{generated/metrics.tex}{
\input{generated/metrics.tex}
}{}
\InputIfFileExists{generated/publications.tex}{
\input{generated/publications.tex}
}{
\item \textit{Run \texttt{python scripts/generate\_cv.py} with a valid ADS token to populate the automated publication list.}
}
\end{cSection}


\begin{cSection}{Grants and Awards}
\vspace{1.8em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{.98\textwidth}{X r}
NASA Postdoctoral Program Fellowship & 2024-2026 \\
Rackham Predoctoral Fellowship & 2023-2024 \\
Rackham Professional Development Grant & 2023 \\
Rackham Graduate Student Research Grant & 2023 \\
Rackham Travel Grant & 2023 \\
Other Worlds Laboratory Summer Program & 2022 \\
NSF Graduate Research Fellowship Program Honorable Mention & 2021 \\
Michigan Space Grant & 2021\\
Jeff Metcalf Fellowship & 2015 \\
University of Chicago Deans List & 2014-2018\\
\end{tabularx}
\end{cSection}


\vspace{0.3em}

\begin{cSection}{Mentoring}
\vspace{2em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{.98\textwidth}{X r}
Elijah Mullens, graduate research & 2024--present \\
Thomas Kennedy, graduate research & 2023--present \\
Alex Wingate, undergraduate research & 2022--2024 \\
Eli Cinque, undergraduate research & 2022--2024 \\
\end{tabularx}
\end{cSection}
\vspace{0.3em}

\begin{cSection}{Teaching}
\vspace{1.6em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{.98\textwidth}{X r}
\textbf{ASTRO 105: Cosmos Constellations} & The University of Michigan\\
\textit{Graduate Student Instructor} & \textit{Spring 2021}\\
\textbf{ASTRO 101: The Solar System and the Search for a New Earth} & The University of Michigan\\
\textit{Graduate Student Instructor} & \textit{Fall 2020}\\
\end{tabularx}
\end{cSection}

\begin{cSection}{Service, Outreach, and Skills}
\renewcommand{\arraystretch}{1.2}
\vspace{1.6em}
\begin{tabularx}{.98\textwidth}{l X}
\textit{Peer Review:} 
& \textit{NASA NSPIRES (2025)} \\
& \textit{The Astrophysical Journal (2025)} \\
& \textit{The Astrophysical Journal Letters (2023)} \\
& \textit{The Journal of Open Source Software (2023)}\\
\textit{Service:}
& Intro2Astro Course Volunteer Summer (2021) \\
& Scarlett Middle School Teaching Assistant (2020) \\
& Science Olympiad Mentor at Slauson Middle School (2020)\\
& Ann Arbor Astronomy on Tap (2019) \\
& Invisible Institute Volunteer Infographic Designer (2018) \\
\textit{Training: } & Exoclimes Summer School (2023) \\
& SC23 Supercomputing Workshops (2023) \\
& University of Chicago Supercomputer Workshops (2018)\\
\textit{Computing:} & Advanced: Python,  FORTRAN 77, FORTRAN 95, git, HPC systems\\ 
 & Basic: C,  OpenMP, Julia, SQL \\
\end{tabularx}
\end{cSection}




\begin{cSection}{Successful Observing Proposals}
\vspace{0.6cm}

\noindent \textbf{[Co-I]}  Meeting their Match: Measuring Cloudy Hot Jupiter Counterparts to Understand the Silicate Cloud Regime with JWST/MIRI - Moran et al., JWST, 46.1 hours (2025)


\noindent \textbf{[Co-I]} The Beginning of a High-Resolution Emission Spectroscopy Program at Magellan for the Characterization of Hot Jupiter Atmospheres with the WINERED Instrument - Sluijs et al., Magellan, 3 nights (2023)

\noindent \textbf{[Co-I]} Tracing the Day-Night Structure of WASP-121b with Multi-Phase High-Resolution Spectroscopy - Rauscher et. al., Gemini South, 12 hours (2023)
  
\noindent \textbf{[Co-I]} Tracing the Day-Night Structure of WASP-76b with Multi-Phase High-Resolution Spectroscopy - Rauscher et. al., Gemini South, 20 hours (2023)

\noindent \textbf{[Co-I]} The First High-Resolution Emission Spectrum of an Exoplanet with WINERED at Magellan - Rauscher et. al., Magellan, 12 hours (2022)
\end{cSection}










\begin{cSection}{Selected Presentations}
\item \textbf{ExSoCal.} Breaking the Accuracy-Speed Trade-off in Radiative Transfer Calculations with Transformer-Based Emulation. 2025. (talk)

\item \textbf{Aspen Rocky Worlds Conference.} Clouds and Hazes in Trappist 1214 b’s Metal-Rich Atmosphere. 2025. (talk)

\item \textbf{NASA AMES.} Machine Learning Emulation of Atmospheric Radiative Transfer. 2025. (talk)

\item \textbf{Cornell.} Clouds and Hazes in GJ 1214b’s Metal-Rich Atmosphere. 2024. (talk)

\item \textbf{NASA Jet Propulsion Lab.} Characterizing Exoplanet Atmospheres: 1D and 3D. 2024. (talk)

\item \textbf{Los Alamos National Lab.} Characterizing Exoplanet Atmospheres: 1D and 3D. 2024. (talk)

\item \textbf{Exoclimes VI.} Clouds and Hazes in Polychromatic General circulation Models. 2023. (talk)

\item \textbf{Bay Area Exoplanets Meeting.} Clouds and hazes in Polychromatic GCMs. 2022. (talk)

\item \textbf{The Other Worlds Laboratory.} A Direct Comparison between a Double Gray and Multiwavelength GCMs. 2022. (talk)

\iffalse
\item \textbf{The University of Michigan Lunch Talks.} Modeling the Three-Dimensional Atmospheric Structure of Hot Gaseous Planets. 2022. (talk)
\fi

\item \textbf{Great Lakes Exoplanet Area Meeting.} Modeling the Three-Dimensional Atmospheric Structure of Hot Gaseous Planets. 2021. (talk)

\item \textbf{Exoplanets IV.} Modeling the
High-resolution Emission Spectra of Clear and Cloudy non-transiting Hot Jupiters. 2020. (poster)

\item \textbf{MIT-Harvard Poster Session} The Coupled Thermal Evolution of sub-Neptune Atmospheres. 2018. (poster)

\item \textbf{The US Naval Academy.} The Coupled Thermal Evolution of sub-Neptune Atmospheres. 2018. (poster)

\end{cSection}


\end{document}
