%-------------------------
% Resume in Latex
% Author : Isaac Malsky
% Adapted from: Sourabh Bajaj, Amlaan Bhoi
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{orcidlink}
\usepackage{setspace}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage[margin=1in]{geometry}
\usepackage{readarray}

% \usepackage[usenames,dvipsnames]{color}

\usepackage{enumitem}
% \usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[utf8]{inputenc}
\input{src/supp_tex/cvstyle}


% \renewcommand{\headrulewidth}{0pt}
% % \pagestyle{fancy}
% \lhead{\deemph{Isaac Baliga Malsky}}
% \chead{\deemph{Curriculum Vitae}}
% \rhead{\deemph{\thepage}}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.50in}
% \addtolength{\evensidemargin}{-0.50in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

\titleformat{\subsection}{
  \vspace{-6pt}\scshape\raggedright \normalsize
}{}{0em}{}[\color{black} \vspace{-5pt}]

\newcommand{\shortershorterSection}[1]{\vspace{-10pt}\subsection{#1}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\begin{document}\thispagestyle{empty}

%----------HEADING-----------------
\begin{center}
  \small \textbf{\large Isaac B. Malsky} \\
  \textsf{\small \href{href="mailto:isaacmalsky@gmail.com"}{isaacmalsky@gmail.com}} $\vert$  \orcidlink{0000-0002-2454-768X} \href{https://orcid.org/0000-0003-0217-3880/}{0000-0003-0217-3880} $\vert$ \href{https://imalsky.github.io/}{https://imalsky.github.io/}
\end{center}
\vspace{-20pt}
%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Michigan}{Ann Arbor, MI}
      {Ph.D., Astronomy}{2024, expected}{
    }
    \vspace{-37pt}
    \resumeSubheading
    {}{}{M.S., Astronomy $\vert$ Advisor: Eliza M.-R. Kempton}{2022}{
    }
    \vspace{-20pt}
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {B.A., Astrophysics; B.A., Physics $\vert$ Advisor: Courtney D. Dressing}{2020}{
    }
  \resumeSubHeadingListEnd


%-----------RESEARCH INTERESTS-----------------
\vspace{-12pt}


%------------PUBLICATIONS-------------------

\shorterSection{Publications}
\input{src/supp_tex/pubs_summary}
\shortershorterSection{\underline{Refereed Publications}}
% \resumeSubHeadingListStart
\small
\begin{list}{}{\cvlist}
    \input{src/supp_tex/pubs_ref_short}
  \end{list}
% \resumeSubHeadingListEnd

\shortershorterSection{\underline{Under review}}
% \resumeSubHeadingListStart
\small
\begin{list}{}{\cvlist}
    \input{src/supp_tex/pubs_submitted.tex}
    \input{src/supp_tex/pubs_unref_short.tex}
\end{list}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\shorterSection{Selected Honors, Prizes, \& Awards}
\small
  \begin{list}{}{\cvlist}
    \input{src/supp_tex/honors}
\end{list}

%-----------Research Talks-----------------
\shorterSection{Science Talks}
\vspace{12pt}
\shortershorterSection{\underline{Invited talks}}
\small
  \begin{list}{}{\cvlist}

  \item[{\color{numcolor}\scriptsize3}] \textbf{Isaac Malsky}, 2023. College of Mathematical and Natural Sciences Board of Visitors. University of Maryland, College Park, MD.

  

  \item[{\color{numcolor}\scriptsize2}] \textbf{Isaac Malsky}, 2023. "Knowing when to know: bridging data-driven and physics-driven modeling for exoplanet atmospheres." Center for Theory and Computation Lunch Talk, Department of Astronomy, University of Maryland, College Park, MD.

   \item[{\color{numcolor}\scriptsize1}] \textbf{Isaac Malsky}, 2021. ``No umbrella needed: Confronting the hypothesis of iron rain on WASP-76b with post-processed general circulation models'', ExoCoffee, MPIA Heidelberg.


  \end{list}

\shortershorterSection{\underline{Contributed Talks}}

\small
  \begin{list}{}{\cvlist}
  

  \item[{\color{numcolor}\scriptsize9}] \textbf{Isaac Malsky}, 2023. "Peering into the black box: 
the uncertainty budget of high-resolution spectroscopy of exoplanet atmospheres." Flatiron CCA Pre-doctoral Symposium, New York, NY.

\item[{\color{numcolor}\scriptsize8}] \textbf{Isaac Malsky}, 2022. ``Phase-resolved asymmetries of (ultra)hot Jupiters in high-resolution transmission: drivers and diagnostics'', Flatiron Exoplanet Atmospheres Symposium, New York, NY.

  \item[{\color{numcolor}\scriptsize7}] \textbf{Isaac Malsky}, 2022. ``Modeling Lorentz drag in an ultra-hot Jupiter over a range of atmospheric parameters'', Burgers Program Research Symposium on Environmental and Applied Fluid Dynamics, The George Washington University.

     \item[{\color{numcolor}\scriptsize6}] \textbf{Isaac Malsky}, 2022. ``Phase-resolved asymmetries of (ultra)hot Jupiters in high-resolution transmission: drivers and diagnostics'', Exoplanets IV, Las Vegas, CA.


   \item[{\color{numcolor}\scriptsize5}] \textbf{Isaac Malsky}, 2022. ``Phase-resolved asymmetries of (ultra)hot Jupiters in high-resolution transmission: drivers and diagnostics'', Bay Area Exoplanet Meeting \#40, NASA Ames.


\item[{\color{numcolor}\scriptsize4}] \textbf{Isaac Malsky}, 2021. ``No umbrella needed: Confronting the hypothesis of iron rain on WASP-76b with post-processed general circulation models'', Astronomy and Space Physics Seminar, University of Kansas.



\item[{\color{numcolor}\scriptsize3}] \textbf{Isaac Malsky}, Courtney D. Dressing, Lea Hirsch, David Ciardi, Jordan P.C. Fleming, Steven Giacalone, Andrew W. Mayo, Jessie L. Christiansen, 2019. “A Closer Look at Exoplanet Occurrence Rates: Considering the Multiplicity of Stars without Detected Planets”, Bay Area Exoplanet Meeting \#31, NASA Ames

\item[{\color{numcolor}\scriptsize2}] \textbf{Isaac Malsky}, Courtney D. Dressing, Lea Hirsch, David Ciardi, Jordan P.C. Fleming, Steven Giacalone, Andrew W. Mayo, Jessie L. Christiansen, 2019. “A Closer Look at Exoplanet Occurrence Rates: The Impact of Stars Without Exoplanets”, Bay Area Planetary Sciences Meeting, Stanford University.

\item[{\color{numcolor}\scriptsize1}] \textbf{Isaac Malsky}, 2019. “Earth: Rare or Regular?”, Undergraduate Seminars, UC Berkeley.

\end{list}

\shorterSection{Research Mentoring}
\small
  \begin{list}{}{\cvlist}  
  \item[{\color{numcolor}}]Kenneth Ellis Arnold III, UMD, College Park (with Prof. Eliza M.-R. Kempton), 2022--present \\
  \textit{Modeling limb asymmetries of cloudy hot Jupiter atmospheres}
  \item[{\color{numcolor}}]Holden Gill, UC Berkeley (with Asst. Prof. Courtney D. Dressing), 2020--2022 \\
    \textit{Ground-based imaging follow-up of K2 planet hosts}


  \end{list}

\shorterSection{Misc. Mentoring}
\small
  \begin{list}{}{\cvlist}
  \item[{\color{numcolor}}]Cole Smith, UMD, College Park, via Undergrad--Grad Mentorship Program, 2023
  \item[{\color{numcolor}}]Yash Gursahani, UMD, College Park, via Astro Grad Buddy Program, 2023
  \item[{\color{numcolor}}]Serena Cronin, UMD, College Park, via Astro Grad Buddy Program, 2021 
  \item[{\color{numcolor}}]Lawrence Edmond IV, UC Berkeley, via Astronomy Buddy Program, 2019


  \end{list} 

  \shorterSection{Selected Community Involvement}
 \begin{list}{}{\cvlist}
\item Graduate student website committee member, University of Maryland, College Park (2023--present)
\item Lead author / maintainer: \href{https://www.IsaacMalsky.com/hires_papers.html}{High-resolution literature database} (2022--present)
\item Graduation Gift Organizer, University of Maryland, College Park (2022--2023)
\item GRAD-MAP Team Co-Lead, University of Maryland, College Park (2022--present)
\item BANG! Seminar Organizing Committee, University of Maryland, College Park (2021--2022)
\item ``Hot Papers'' journal club organizer, University of Maryland, College Park (2020--2022)
\item Reviewer, Journal of Open Source Software (3 projects reviewed) (2020--present)
\item Equity, Diversity, and Inclusion Committee, University of Maryland, College Park (2020--2022)
\item Public Liaison for Prof. Alex Filippenko (2019--2022)
\item Undergraduate Representative, Astronomy Department, UC Berkeley (2019-2020)
\item Director of Physics and Astronomy, Undergraduate Lab at Berkeley (ULAB) (2018-2019)
 \end{list} 

\end{document}
