\documentclass{cv}
\usepackage[utf8]{inputenc}
\usepackage[left=0.75in,top = 0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[dvipsnames]{xcolor}


\usepackage{fancyhdr,tabularx}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyhead[R]{\textit{updated \today}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{14pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{changepage}
\name{Marianne Cowherd}
\phone{\href{mariannecowherd.github.io}{mariannecowherd.github.io}}
\email{cowherd@berkeley.edu}
\address{222 Mulford Hall, University of California, Berkeley}
\renewcommand{\familydefault}{\sfdefault} %edit this for fonts›

\begin{document}
\begin{cSection}{Education}
\begin{cSubsection}{\vspace{1.6em} Ph.D. candidate, Environmental Science, Policy, and Management (ESPM)} {UC Berkeley} {\normalfont{Dissertation: ``Climate change and wildland fire effects on snow''}} {expected 2025  }
\item Committee: Manuela Girotto, Scott Stephens, Lara Kueppers, \& Andrew Schwartz
\end{cSubsection}
\begin{cSubsection}{M.S., Environmental Engineering} {Stanford University, 2020} {\normalfont{Environmental Fluid Mechanics and Hydrology}}{  }
\item  \textcolor{white}{whitespace} \vspace{-2em}
\end{cSubsection}
\begin{cSubsection}{B.S., Environmental Systems Engineering, honors} {Stanford University, 2019} {\textcolor{white}{whitespace}}{  }
\item  \textcolor{white}{whitespace} \vspace{-2em}
\end{cSubsection}
\end{cSection}
\vspace{-0.2cm}
\begin{cSection}{Appointments}
\begin{cSubsection}{\vspace{1.6em}Girotto Lab \& Stephens Lab, UC Berkeley}
  {Berkeley, California}{US DOE Computational Science Graduate Fellow (2021-25)}{2020--present }
  \item \textit{Research associate, Central Sierra Snow Laboratory (2021-2025)}
  % \item \textit{Berkeley Artificial Intelligence Research Climate Initiative}
\end{cSubsection}
\begin{cSubsection}{Lawrence Berkeley National Laboratory}
  {Berkeley, California}{Affiliate, Earth and Environmental Sciences Area}{2023--present }
\item  \textcolor{white}{whitespace} \vspace{-1em}
% \item \textit{Supervisor: Daniel Feldman}
%   \item \textit{Surface Atmosphere Integrated Field Laboratory (SAIL)}
\end{cSubsection} 
\begin{cSubsection}{Pacific Northwest National Laboratory}
  {Richland, Washington}{Visiting Researcher, Earth Systems Analysis \& Modeling}{2022 }
\item  \textcolor{white}{whitespace} \vspace{-1em}
  % \item \textit{Supervisor: L. Ruby Leung}
\end{cSubsection} 
\begin{cSubsection} {Bob \& Norma Street Environmental Fluid Mechanics Lab}{Stanford, California}{Research Assistant}{2018-2020 }
\item  \textcolor{white}{whitespace} \vspace{-1em}
\end{cSubsection}
%\begin{cSubsection}{miRcore}{Ann Arbor, Michigan}
%{Data Scientist (2014-19, \textit{ad hoc}), Summer Programs Co-Director (2019)}{2014-2019 }
%\item  \textcolor{white}{whitespace} \vspace{-1em}
% \end{cSubsection}
\end{cSection}
\vspace{-0.2cm}
%\newpage
\begin{cSection}{Publications}
\IfFileExists{generated/publications.tex}{
  \input{generated/publications.tex}
}{
  \item Run \texttt{python src/generate\_cv.py} to populate the generated publications list.
}
\end{cSection}
\begin{cSection}{Grants, Fellowships \& Awards}
\vspace{1.6em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{.98\textwidth}{X r}
ELLIIT (Sweden) Machine Learning for Climate Science visiting scholar grant & 2024 \\ % (\textit{\$3000})
Alpine Avalanche Rescue Foundation Training Scholarship & 2024 \\ % (\textit{\$900})
UC Berkeley Graduate Division Conference Travel Grant & 2024 (x2) \\ % (\textit{\$900; \$1,500})
Peder Sather Grant (Co-I) & 2023-2025 \\ % (\textit{\$20,000})
H2H8 Undergraduate Researcher Support Grant & 2023 \\ % (\textit{\$3,500})
H2H8 Graduate Student Explorer Grant & 2022 \\ % (\textit{\$10,000})
NCAR University Small Request & 2022 \\ % (\textit{105,000 core-hours})
US Department of Energy Computational Science Graduate Fellowship & 2021-2025 \\ % \textit{(∼\$256,000)}
UC Berkeley Sponsored Programs for Undergraduate Research & 2021-23 \\ % \textit{(\$1,000)}
UC Berkeley Forestry Research Summer Award & 2021 \\ % \textit{(\$6,000)}
UC Berkeley Undergraduate Mentoring Fellowship & 2021 \\ % \textit{(\$10,000)}
UC Berkeley Graduate Remote Instruction Innovation Fellowship & 2020-2021 \\ % \textit{(\$2,000)}
UC Berkeley ESPM Starter Grant & 2020 \\ % \textit{(\$1,000)}
UC Berkeley STEM*FYI Technology Grant & 2020 \\ % \textit{(\$500)}
NSF GRFP honorable mention & 2019 \\
Stanford Undergraduate Conference Grant & 2019 \\ % \textit{(\$1,500)}
Stanford Undergraduate Summer Research Fellowship & 2018 \\ % \textit{(\$7,000)}
Stanford Woods Institute Forum for Undergraduate Environmental Leadership & 2018 \\
\end{tabularx}
\end{cSection}

\begin{cSection}{Invited Talks}
\item ``Snow measurements in a changing climate: from ground observations to machine learning.'' Berkeley Atmospheric Sciences Center Seminar, April 2025, Berkeley, California.
\item ``Snow measurements in a changing climate: from ground observations to machine learning.'' Montana State University Earth Sciences Seminar, February 2025, Bozeman, Montana.
\item ``Snow measurement representativeness after the Caldor Fire.'' California Cooperative Snow Surveys Meeting, November 2024, Auburn, California.
\item ``Climate-resilient snowpack estimation.'' Machine Learning for Climate Science Seminar Series, Link\"oping University, October 2024, Link\"oping, Sweden.
\item ``How will we use snowpack measurements in a warmer future?'' GeoHyd Seminar, September 2024, University of Oslo, Oslo, Norway.
\item ``Snow physics and statistics: education and research.'' Outer Coast College, November 2023, Sitka, Alaska. 
\item  ``Remote monitoring of snow water resources.'' Satellite Data for Hydrological Applications Seminar, Groupement de recherche international-Sud: Risques Hydrologiques au Maghreb, September 2022, virtual.
\end{cSection}

\begin{cSection}{First-Author Conferences}
\item \textbf{Cowherd, M.}, Gutmann, E., and Feldman, D. ``Snow bedforms observed with terrestrial scanning lidar'' Joint ARM User Facility and ASR PI Meeting, March 2025, Rockville, MD. (poster)
\item \textbf{Cowherd, M.}, Gibson, L., Feldman, D., Aiken, A., Riihimaki, L., Telg, H., Hodshire, A., Levin, E., and McMeeking, G., ``Inferring wet deposition (of dust)'' Joint ARM User Facility and ASR PI Meeting, March 2025, Rockville, MD. (talk)
\item \textbf{Cowherd, M.}, Mital, U., Rahimi, S., Girotto, M, Schwartz, A., and Feldman, D.  ``Climate-resilient snowpack estimation: measurements and models in a changed future'' American Geophysical Union, December 2024, Washington, D.C. (invited talk)
\item \textbf{Cowherd, M.}, Gutmann, E., Kochanski, K., and Feldman, D.  ``Snow bedforms observed with terrestrial scanning lidar'' American Geophysical Union, December 2024, Washington, D.C. (poster)
\item \textbf{Cowherd, M.}, et al.  ``Climate-resilient snowpack estimation with machine learning'' NCAR-CISL International Computing in the Atmospheric Sciences Symposium, September 2024, Stresa, Italy. (talk)
\item \textbf{Cowherd, M.}, Schwartz, A., Marks, J., Brandt, G., Kim, L., Collins, B., Stephens, S., and Girotto, M. ``Post-fire accumulation and melt in the Caldor Fire'' Western Snow Conference, April 2024, Corvallis, Oregon. (talk)
\item \textbf{Cowherd, M.}, Rahimi, S., Girotto, M. ``Predicting spatio-temporal distribution of snow droughts using dynamically downscaled, high resolutions climate models'' American Geophysical Union, December 2023, San Francisco, California. (poster) 
\item \textbf{Cowherd, M.}, Mital, U., Rahimi, S., Duan, S., Girotto, M., and Feldman, D. ``Future changes in Western US snow distribution predictability: the case for using multi-modal observations within artificial intelligence models'' American Geophysical Union, December 2023, San Francisco, California. (poster)
\item \textbf{Cowherd, M.}, Gutmann, E., and Feldman, D. ``What can we learn about snow bedforms from lidar scans at Kettle Ponds?'' S3 Science Workshop, November 2023, Boulder, Colorado. (talk)
\item \textbf{Cowherd, M.}, Reed, C.J., Duan, S., Rahimi, S., Mital, U., Girotto, M., and Feldman, D. ``ML for climate-change resilient snowpack estimation in the Western United States'' HydroML Symposium, May 2023, Berkeley, California. (breakout talk)
\item \textbf{Cowherd, M.}, Leung, L.R., and Girotto, M. ``Snow droughts in E3SM'' American Geophysical Union, December 2022, Chicago, Illinois. (poster)
\item \textbf{Cowherd, M.}, Trujillo, E., and Girotto, M. ``Snow-wildland fire feedbacks in the Sierra Nevada'' Western Snow Conference, April 2022, Salt Lake City, Utah. (poster)
\item \textbf{Cowherd, M.} and Girotto, M. ``Snow-productivity relationships in the fire-impacted Sierra Nevada'' American Geophysical Union, December 2021, New Orleans, Louisiana and virtual. (talk)
\item \textbf{Cowherd, M.}, Baldocchi, D., and Girotto, M. ``Energy flux over snow during melt season'' AmeriFlux Annual Meeting, September 2021, virtual. (poster)
\item \textbf{Cowherd, M.}, Egan, G., Monismith, S. G., and Fringer, O. ``Wave phase-decomposed near-bed currents and turbulence on the shoals of South San Francisco Bay'' Ocean Sciences Meeting, February 2020, San Diego, California. (poster)
\item \textbf{Cowherd, M.}``Use of the Hilbert transform in spectral analysis of wave-current flows'' Environmental Fluid Mechanics Laboratory Seminar, May 2019, Stanford, California. (talk)
\end{cSection}

\begin{cSection}{Teaching}
\vspace{1.6em}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{.98\textwidth}{X r}
\textbf{University of California, Berkeley } & \\
\textit{Seminar Lead} & \\
ESPM 290: Comunicando Ciencias Ambientales y de la Salud & Fall 2022 \\
\textit{Graduate Student Instructor} & \\
GEOG 185: Earth System Remote Sensing & Spring 2021 \\
ESPM 15: Introduction to Environmental Sciences & Fall 2020 \\
\textit{Guest Lectures} & \\
``Wildland fire interactions with hydrology and aquatic ecosystems'' & Fall 2023 \\
\end{tabularx}
\begin{tabularx}{.98\textwidth}{X r}
\textbf{Stanford University } & \\
\textit{Course Assistant} & \\
EARTHSYS 10: Introduction to Earth Systems Engineering & Fall 2019\\
CEE 1: Introduction to Environmental Systems Engineering & Spring 2019\\
\textbf{Field Courses} & \\
CUAHSI/SINTER Snow Measurements Field School & January 2025 \\
Central Sierra Snow Lab Snow Science School & Janurary 2025\\
\end{tabularx}

% \begin{tabularx}{.98\textwidth}{X r}
% \textbf{CSSL Snow Science School} & CSSL\\
% \textit{Teaching Assistant} & \textit{Winter 2025}\\
% \textbf{Snow Measurement Field Course} & SINTER/CUAHSI\\
% \textit{Teaching Assistant} & \textit{Winter 2025}\\
% \textbf{ESPM 181: Fire Ecology} & UC Berkeley\\
% \textit{Guest lecturer: Wildland fire interactions with hydrology and aquatic ecosystems} & \textit{Fall 2023}\\
% \textbf{ESPM 290: Comunicando Ciencias Ambientales y de la Salud} & UC Berkeley\\
% \textit{Co-creator and instructor} & \textit{Fall 2022}\\
% \textbf{GEOG 185: Earth System Remote Sensing} & UC Berkeley\\
% \textit{Graduate Student Instructor} & \textit{Spring 2021}\\
% \textbf{ESPM 15: Introduction to Environmental Sciences} & UC Berkeley\\
% \textit{Graduate Student Instructor} & \textit{Fall 2020}\\
% \textbf{Indigenizing Futures} & Outer Coast\\
% \textit{Summer Seminar Advisor} & \textit{Summer 2020}\\
% \textbf{EARTHSYS 10: Introduction to Earth Systems}& Stanford University\\
% \textit{Course Assistant}& \textit{Fall 2019}  \\
% \textbf{CEE 1: Introduction to Environmental Systems Engineering} & Stanford University\\
% \textit{Course Assistant}& \textit{Spring 2019}
% \end{tabularx}


\end{cSection}

\begin{cSection}{Mentoring}
\renewcommand{\arraystretch}{1.2}
\vspace{1.6em}
\begin{tabularx}{.98\textwidth}{X r}
% Mina Kim, undergraduate thesis & 2023-present \\
Mia Jones, CSSL instrumentation project & 2024 \\
Gisele Brandt, undergraduate research & 2023-present\\
Lee Kim, undergraduate research & 2023-present \\
Shashwath Senthil, Berkeley AI intern & 2023-present\\
% Alia Franczyk, Central Sierra Snow Lab undergraduate research & 2023-24\\
Evan Robert, H2H8 undergraduate fellow ($\rightarrow$Luna Energy) & 2023-24\\
% Megan Mehta, Data Science Discovery undergraduate student & 2023 \\
% Sara Yavas, Data Science Discovery undergraduate student & 2023 \\
Julia Marks, undergraduate research ($\rightarrow$USFS wildland fire module) & 2022-23\\
Sarah Zhang, undergraduate thesis ($\rightarrow$Caltech PhD) & 2021-23\\
Jieyuan Kan, undergraduate summer research fellow ($\rightarrow$UN Environment) & 2021 \\
Hayden Street, undergraduate thesis ($\rightarrow$Taylor Environmental) & 2020-21\\
\end{tabularx}
\end{cSection}


\begin{cSection}{Service and Outreach}
\renewcommand{\arraystretch}{1.2}
\vspace{1.6em}
\begin{tabularx}{.98\textwidth}{l X}
\textit{Peer Review:} &  \textit{Environmental Research Letters}, \textit{Journal of Climate}, \textit{Geophysical Research Letters}, \textit{Water Resources Research}, \textit{Journal of Hydrology}, \textit{Geophysical Model Development}, \textit{npj Climate and Atmospheric Science}, \textit{Communications Earth \& Environment}\\
\textit{Proposal:} & Climate Change AI Innovation Grants \\
\textit{Conference:} & HydroML Symposium session lead, ``Machine learning for predicting streamflow'' (2023)\\
\textit{University:} 
& Faculty search committee (2024) \\ 
& Graduate admissions committee (2023) \\
 & Chancellor's Advisory Committee on Sustainability and Climate Change (2022-2023) \\
 & Faculty Senate Diversity, Equity, and Campus Climate Committee (2021-2022)\\
 & Graduate Assembly (2021-2023) \\
& ESPM Mentoring Faculty Working Group (2020-2021)\\
\textit{Outreach: } & Black Pine Circle 5th grade science slam, presenter (2023) \\
& Ann Arbor Public Schools English Learner Program, volunteer (2020-2021)\\
& YouBelong/Pertenecer STEM Outreach Program, volunteer (2019)\\
& Jasper Ridge Biological Preserve, naturalist docent (2018-2021)\\
 \textit{Memberships:} &American Geophysical Union \\
& Association for Computing Machinery High Performance Computing (SIGHPC) \\
& Association for Fire Ecology\\
\end{tabularx}
\end{cSection}

\begin{cSection}{Skills}
\renewcommand{\arraystretch}{1.2}
\vspace{1.6em}
\begin{tabularx}{.98\textwidth}{l X}
\textit{Computing:} & Python, R, MATLAB, C++, bash, Fortran 90, Google Earth Engine, \LaTeX, git, QGIS, ENVI,  parallel computing (OpenMP, MPI, CUDA) \\
\textit{Training: } & INTERSECT Research Software Engineering Bootcamp (2024) \\
 \textcolor{white}{Memberships:} & USDA SWF Climate Adaptation Science Academy Experiential Learning Expedition (2024) \\ 
& EGU Snow Science Winter School (2023) \\
&UC Berkeley Certificate of Teaching and Learning in Higher Education (2021) \\
& UNAVCO InSAR Short Course (2021) \\
& SnowEx HackWeek, University of Washington (2021) \\
 \textit{Field:} & snow field measurements, hydrodynamics instrumentation, forestry and vegetation, winter backcountry travel (ski, snowmobile), eddy covariance \\
 & AIARE 2, Wilderness First Aid, PADI Open Water Dive \\ 
 \textit{Languages:} & English (fluent), Spanish (proficient), French (proficient) \\
\end{tabularx}
\end{cSection}

\begin{cSection}{Field Experience}
\renewcommand{\arraystretch}{1.2}
\vspace{1.6em}
\begin{tabularx}{.98\textwidth}{>{\raggedright\arraybackslash}X  r}
\textbf{Gothic, Colorado} -- DOE Surface Atmosphere Integrated Field Laboratory. Funded by NASA SnowEx (PI Daniel Feldman). & April 2024 \\
\textbf{Fairbanks, Alaska} -- NASA SnowEx Albedo Alaska campaign. Timed field spectrometer surveys in burned areas contemporary with AVIRIS overflights. Funded by NASA SnowEx (PIs Anne Nolin and Kelly Gleason). & April 2023 \\
\textbf{Caldor Fire, California} -- Lead. Winter season snow depth monitoring from camera time-lapse throughout the burned area. Funded by H2H8 grant (Cowherd). & 2022-2024\\
\textbf{Illilouette Creek Basin, California} -- Fire ecology and forestry measurements, Yosemite National Park. (PIs Scott Stephens and Gabrielle Boisram\'e). & Summer 2021\\
\textbf{South San Francisco Bay, California} -- Assistant on hydrodynamics campaign for underwater instrumentation installation and collection. Constructed, deployed, and retrieved instrument arrays. Funded by NSF grant (PIs Oliver Fringer and Stephen Monismith) and Stanford CEE undergraduate grant (Cowherd). & May-August 2019 \\
\textbf{Nikko Bay, Palau}  -- Assistant on hydrodynamics campaign for underwater instrumentation installation and seagrass community survey. (Lead: Heidi Hirsh) & June 2017 \\
% \textbf{Durango, Colorado}  -- USFS seasonal wilderness ranger. Crosscut saw, backcountry travel with pack animals. (USDA/San Juan Mountain Association) & May-September 2016 

\end{tabularx}
\end{cSection}


%\begin{cSection}{References}
%\vspace{1.6em}
% \textbf{Manuela Girotto} \\
% Associate Professor, UC Berkeley\\
% Department of Environmental Science, Policy, and Management\\
% mgirotto@berkeley.edu \\
% +1 (310) 806-3767 \\
% % \textbf{Scott Stephens} \\
% % Professor, UC Berkeley\\
% % Department of Environmental Science, Policy, and Management\\
% % sstephens@berkeley.edu \\
% \\ 
% \textbf{Daniel Feldman} \\
% Staff Scientist, Lawrence Berkeley National Laboratory\\
% Earth and Environmental Sciences Area\\
% drfeldman@lbl.gov \\
% +1 (626) 482-6839 \\
% \\ 
% \textbf{Andrew Schwartz} \\
% Director, Central Sierra Snow Lab\\
% aschwartz@berkeley.edu \\
% +1 (530) 536-8790
% \\ 
% \textbf{Jeff Chambers} (teaching)\\
% Professor, UC Berkeley\\
% Department of Geography\\
% jqchambers@berkeley.edu \\
%\end{cSection}


\end{document}
